Codebook
========
Codebook was generated on `r as.character(Sys.time())` during the same process that generated the dataset.

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subjectNum       | IDs the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r echo=FALSE} 
str(finalData)
```


Key variables in the data table
----------------------------------------

```{r echo=FALSE}
key(finalData)
```

A few rows of the dataset
------------------------------

```{r echo=FALSE}
finalData
```

Summary of variables
--------------------

```{r echo=FALSE}
summary(finalData)
```

All possible combinations of features
------------------------------------------

```{r echo=FALSE}
finalData[, .N, by=c(names(finalData)[grep("^feat", names(finalData))])]
```

Data saved to a tab-delimited text file called "HumanActivityRecognitionData.txt"
---------------------------------------------------------------------------------

```{r echo=FALSE}
fread(file.path(getwd(), "HumanActivityRecognitionData.txt"))
```
